### 2020-06-01 README.Rmd
GitHub actions
some unit tests :construction:

<!-- badges: start -->
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R build status](https://github.com/cboettig/neonstore/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/neonstore/actions)
[![Codecov test coverage](https://codecov.io/gh/cboettig/neonstore/branch/master/graph/badge.svg)](https://codecov.io/gh/cboettig/neonstore?branch=master)
<!-- badges: end -->
